To Compete or Cooperate? This is the Question in Communities of Autonomous Services

### 2014-02-23 papers/coop-journal-R1/coop_response_letter.tex

\vspace{0.5cm}\textbf{\underline{2. Reviewer}:}  In section 2.2 (system parameters), the authors should specify how many parameters are used before explaining them and using such parameters in the proposed mathematics. This should aid the reader in better understanding.

\vspace{0.2cm}\textbf{\underline{Answer 2}: In the revised version, we added a short summary about the system parameters in section 2.2. We have five system parameters \emph{Task QoS}, \emph{Service QoS}, \emph{Budget}, \emph{Reputation} and \emph{Growth Factor}) and the other variables are derived or calculated based on these five parameters which are listed in Table 1. The title for Table 1. which was ``List of proposed system parameters'' was not very appropriate. We changed its title to ``List of abbreviations''}

\vspace{0.5cm}\textbf{\underline{3. Reviewer}:} The text consists on very long paragraphs, mainly section 4 (experimental results), which makes the reading difficult.

\vspace{0.2cm}\textbf{\underline{Answer 3}: We edited the text in the revised version and made some paragraphs shorter to improve readability of paper.}

@@

\vspace{0.5cm}\textbf{\underline{4. Reviewer}:} Still in section 4, the simulation application should be better specified, adding information on used machine, architecture, most important used services, etc.

\vspace{0.2cm}\textbf{\underline{Answer 4}: We agree. In the revised manuscript, we added more explanations and details about the architecture and service types. Web services were modeled as a \emph{class} and using \emph{Await} and \emph{Async} models we initiated many web services, each running as a thread. We implemented XML based messaging system (like SOAP) with request parameters and a list of XML based responses. The request
contains the flight dates, the origin and destination, type of tickets, and number of guests. The response contains different flights with different companies, prices, timing, etc. We have gathered around 200,000 flights and stored them in our MongoDB database. A pool of web services was initiated and had their \emph{QoS} parameters populated based on the dataset of 2,507 real services functioning on the web.
}

@@

\vspace{0.5cm}\textbf{\underline{5. Reviewer}:} Figure 3 is misplaced.

\vspace{0.2cm}\textbf{\underline{Answer 5}: True. In the revised manuscript, we replaced the Figure at the correct position (we put it after the paragraph it was first mentioned on) and double checked all other figures and tables placements.}

@@

\vspace{0.5cm}\textbf{\underline{1. Reviewer}:}  Abstract: In my opinion, it is not necessary to talk about the sample used.

\vspace{0.2cm}\textbf{\underline{Answer 1}: True, as argued in our Answer 1 to Reviewer 1, We made the abstract more compact and removed some unnecessary details. }

\vspace{0.5cm} \textbf{\underline{2. Reviewer}}:  Introduction: The first phrase ``Services are software systems...'' should include which kind of services are being analysed: intelligent, autonomous,... The definition used does not correspond to ``Services'' as a whole.

\vspace{0.2cm}\textbf{\underline{Answer 2}: We agree, the definition was too broad we rephrased
the sentence as follows: Online Services are software systems providing a standard way of
interoperability among different applications. These services are developed
 as autonomous and intelligent agents and they continuously and autonomously interact with each other to
fulfill users' requests.}

### 2014-02-23 papers/coop-journal-R1/BNJ Exp Sys App.tex
changes

\section{Introduction}\label{Introduction}
\textbf {Online Services are software systems providing a standard way of
interoperability among different applications. These services are developed
 in an autonomous and intelligent manner to continuously and autonomously interact with each other to
fulfill users' requests.} Organizing services within virtual
structures called \emph{communities} has been proposed for the
purpose of making their discovery easier and increasing the
likelihood of their cooperation
\cite{Benatallah2003,Maamar2009,Medjahed2007,Medjahed2005}. The
idea behind communities is to gather services having similar
functionalities but distinct non-functional properties. In that
context, communities are providing pockets of expertise and
networks of services able to cooperate by substituting each other
in case of execution problems
\cite{Bentahar2008,Maamar2009,Mhamdi2012}.

@@

In this section, we provide an empirical analysis over the
theoretical results regarding the characteristics of intelligent
service agents hosted in different communities of services. In the
implemented system, we simulate the behaviors of service consumers
as request generators, service agents as service providers, and
master agents as community representatives. These entities are
developed with respect to what is explained in Section
\ref{Preliminaries}. In this section, the objective is to
investigate the effectiveness of the proposed strategic system on
intelligent services' overall budget and also the average quality
and quantity of tasks performed by the community of services,
which directly affects user satisfaction.
%Before conducting the simulation, the
%expected behavior of our model is to enhance the budget of web
%services when using our proposed strategic interacting system.
%Although this result is promising, we would like to investigate
%the effectiveness of the proposed strategic system on intelligent
%web services' overall budget compared to the best case. Moreover,
To verify these objectives, we study the overall performance of
the community hosting the reasoning-empowered services compared to
the ones hosting stochastic and purely competitive services. By
stochastic services, we mean services that adopt at each moment
competitive or cooperative strategies in an equally but random
way. By equally, we mean the choices are fairly divided between
the two strategies. 
\textbf{The simulation application is written in
\textit{C\#} using \textit{Visual Studio} and executed the implementation on an Intel Xeon X3450 machine with 6GBs of memory.}
 Developed services are
initialized with values taken from a real dataset that includes
$2507$ real services functioning on the web. The dataset records
the QoS values of $9$ parameters including \textit{availability},
\textit{throughput}, and
\textit{reliability} \cite{Almasri}.  %These QoS values
%are determined by monitoring the web services over a $6$-day
%period.

>>>>

\section{Introduction}\label{Introduction}
\textbf {Online Services are software systems providing a standard way of
interoperability among different applications. These services are developed
 as autonomous and intelligent agents and they continuously and autonomously interact with each other to
fulfill users' requests.} Organizing services within virtual
structures called \emph{communities} has been proposed for the
purpose of making their discovery easier and increasing the
likelihood of their cooperation
\cite{Benatallah2003,Maamar2009,Medjahed2007,Medjahed2005}. The
idea behind communities is to gather services having similar
functionalities but distinct non-functional properties. In that
context, communities are providing pockets of expertise and
networks of services able to cooperate by substituting each other
in case of execution problems
\cite{Bentahar2008,Maamar2009,Mhamdi2012}.

@@

In this section, we provide an empirical analysis over the
theoretical results regarding the characteristics of intelligent
service agents hosted in different communities of services. In the
implemented system, we simulate the behaviors of service consumers
as request generators, service agents as service providers, and
master agents as community representatives. These entities are
developed with respect to what is explained in Section
\ref{Preliminaries}. In this section, the objective is to
investigate the effectiveness of the proposed strategic system on
intelligent services' overall budget and also the average quality
and quantity of tasks performed by the community of services,
which directly affects user satisfaction.
%Before conducting the simulation, the
%expected behavior of our model is to enhance the budget of web
%services when using our proposed strategic interacting system.
%Although this result is promising, we would like to investigate
%the effectiveness of the proposed strategic system on intelligent
%web services' overall budget compared to the best case. Moreover,
To verify these objectives, we study the overall performance of
the community hosting the reasoning-empowered services compared to
the ones hosting stochastic and purely competitive services. By
stochastic services, we mean services that adopt at each moment
competitive or cooperative strategies in an equally but random
way. By equally, we mean the choices are fairly divided between
the two strategies.

\textbf{The simulation application is written in
\textit{C\#} using \textit{Visual Studio}. We performed the implementation on a single Intel Xeon X3450 machine with 6GBs of memory. Web services were modeled as a \emph{class} and using \emph{Await} and \emph{Async} models we initiated many web services, each running as a thread.  We implemented XML based messaging system (like SOAP) with request parameters and a list of XML based responses. The request
contains the flight dates, the origin and destination, type of tickets, and number of guests. The response contains different flights with different companies, prices, timing, etc. We have gathered around 200,000 flights and stored them in our MongoDB database.  A pool of services are initialized with values taken from a real dataset that includes $2507$ real services functioning on the web.} 
The dataset records the QoS values of $9$ parameters including \textit{availability},
\textit{throughput}, and \textit{reliability} \cite{Almasri}.  %These QoS values
%are determined by monitoring the web services over a $6$-day
%period.
